---
title: "Sourcing Boston Hackathon Project, Team Gourmet Disco Apocalypse"
author: "Sara Williams"
date: "11/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#From Boston to Hong Kong: The Impact of Climate Change and Extreme Weather Events on Food Access and Prices
Link to presentation: https://docs.google.com/presentation/d/1ISf1QxBqlCWctK_5Gzr-e8nxVNTNfA4bXQAuN4jxCa8/edit#slide=id.g47dd8785b0_0_80 

##The Event: https://github.com/briromer/sourcingboston
Sourcing Boston

## Team Members
Team members day 1: Cat Anderson, Don Blair, Lisa Button, Kevin Huang, Katrina Miller, Aaron Pradhan, Pankaj Shah, Daisy Tam, Sara Williams

Team members day 2: Cat Anderson, Don Blair, Lisa Button, Kevin Huang, Pankaj Shah, Daisy Tam, Sara Williams

##Our Process:



##The Impact of Sea level Rise on Boston's Food Security



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
